### 2022-11-13 NSF2022/Description/backgroundv3.tex
fix typo
yny 1113b

We recently developed a new mathematical model of
self-organization in fluid systems~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
The framework uses small, rigid bodies called ``granules''
to represent parcels of a suspended media.
The granule shapes and boundary conditions
capture the local properties of the suspension,
and instead of volume fraction, a phase field function represents
the properties of the solvent.
Our approach falls into the category of work that considers
particles as a discretization of a continuous problem;
in this case one is dealing with a particle
method, as an alternative to other discretization methods
such as finite-difference, finite-element, and spectral methods
\cite{Wilson2021ComparisonOT}.
We have departed from the terminology
``particles'', though, to emphasize the role played the granules' finite size.

The framework is robust, flexible, and
cuts across many of the aforementioned challenges.
(i) The granules are not fixed to a stencil, 
affording flexibility in terms of morphology and topology---sufficiently
large forces will even pull granules apart as physically required.
(ii) The model formulation is built around important details like molecular orientations,
and exhibits inter-molecular slip that must be added into diffusive interface models
post hoc. 
(iii) It is straightforward to consider mixtures of granules with different
types of shapes and boundary conditions.
Leveraging boundary and fast summation methods, the dynamics can be solved in 
near-linear complexity in the number of granules,
which is equal to or better than 
the computational complexity of related sharp interface methods.

@@

\subsection{Applications}
Since the framework is scale independent, it can be applied broad range
of nonspecific self-organization phenomena in surface chemistry, biology
and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
can be further investigate (\S\ref{sec:specificaim3}).

A concrete application we have considered in our
SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
\cite{Fu2018_SIAM, FuQuRyYo22}
is the problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
The goal in vesicle hydrodynamics is to study the flow patterns 
that arrise due to the interaction
between membrane elasticity and the fluid.

A striking aspect of our hydrodynamic
simulation is its fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When set to realistic values in the literature
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}.

\begin{wrapfigure}[10]{l}{0.46\textwidth}
\includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}

In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of an continous, inextensible, elastic vesicle
with permeability. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading vesicle
\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction were in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear rate
\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
granule-based vesicles and the sharp interface representation yielded
shapes and trajectories that overlapped.

@@

Having a non-specific model that replicates physical details
is the crown jewel of applied mathematics.
\emph{Further applications} include
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
\begin{wrapfigure}[8]{l}{2.1in}
  \vspace{-5pt}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

@@

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \begin{split}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx, \\
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
  \end{split}
\end{align}
%\begin{align}
%\label{eq:energy_law}
%  \frac{d}{dt}E
%  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
%  \uu^T|^2 \,d\xx,\quad
%    E = \gamma \int_{\Omega(t)}
%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
%\end{align}
Here $E$ is the energy stored in the phase transitions
and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations. Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the self-assembly process to
the collective dynamics of the assembly under external forcing.
\begin{wrapfigure}[16]{r}{4in} 
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-20pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties the
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
  \vspace{5pt}
\end{wrapfigure}

>>>>

The PIs recently developed a new mathematical model of
self-organization in fluid systems~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
The framework uses small, rigid bodies called ``granules''
to represent parcels of suspended media.
The granule shapes and boundary conditions
capture the local properties of the suspension,
and instead of volume fraction, a phase field function represents
the properties of the solvent.
Our approach falls into the category of work that considers
particles as a discretization of a continuous problem;
in this case one is dealing with a particle
method, as an alternative to other discretization methods
such as finite-difference, finite-element, and spectral methods
\cite{Wilson2021ComparisonOT}.
We have departed from the terminology
``particles'', though, to emphasize the role played the granules' finite size.

The framework is robust, flexible, and
cuts across many of the aforementioned challenges.
(i) The granules are not fixed to a stencil, 
affording flexibility in terms of morphology and topology---sufficiently
large forces will even pull granules apart as physically required.
(ii) The model formulation is built around important details like molecular orientations,
and exhibits inter-molecular slip that must be added into diffusive interface models
post hoc. 
(iii) It is straightforward to consider mixtures of granules with different
types of shapes and boundary conditions.
Leveraging boundary integral and fast summation methods, the dynamics can be solved in 
near-linear complexity in the number of granules,
which is equal to or better than 
the computational complexity of related sharp interface methods.

@@

\subsection{Applications}
Since the framework is scale independent, it can be applied broad range
of nonspecific self-organization phenomena in surface chemistry, biology
and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
can be further investigate (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in our
SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
\cite{Fu2018_SIAM, FuQuRyYo22}
is the problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
The goal in vesicle hydrodynamics is to study the flow patterns 
that arrise due to the interaction
between membrane elasticity and the fluid.

A striking aspect of our hydrodynamic
simulation is its fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When set to realistic values in the literature
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we quantitatively recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}. 
Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
correctly capture the long-range interactions between amphiphilic granules (such as lipid macromolecules) surfaces.

\begin{wrapfigure}[9]{l}{0.46\textwidth}
\vspace{-10pt}
\includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of an continous, inextensible, elastic vesicle
with permeability. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading vesicle
\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction were in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear rate
\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
granule-based vesicles and the sharp interface representation yielded
shapes and trajectories that overlapped.

@@

Having a non-specific model that replicates physical details
is the crown jewel of applied mathematics.
\emph{Further applications} include
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
\begin{wrapfigure}[9]{l}{2.1in}
  \vspace{-5pt}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

@@

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \begin{split}
  \frac{d}{dt}E
    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx, \\
    E &= \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
  \end{split}
\end{align}
%\begin{align}
%\label{eq:energy_law}
%  \frac{d}{dt}E
%  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
%  \uu^T|^2 \,d\xx,\quad
%    E = \gamma \int_{\Omega(t)}
%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
%\end{align}
Here $E$ is the energy stored in the phase transitions
and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations. Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the self-assembly process to
the collective dynamics of the assembly under external forcing.
\begin{wrapfigure}[16]{r}{4in} 
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-20pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties of
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
  \vspace{5pt}
\end{wrapfigure}
